### 2025-01-29 scripts/Paper-analysis.Rmd
new analysis leading vs. lagging

scores_df = read.csv('../test_bokz_k5_scores.csv', header=T)
scores_average <- scores_df %>%
  rowwise() %>%
  mutate(score_avg = mean(c_across(starts_with("score")))) %>%
  ungroup() %>%
  select(kmer, score_avg)  
# Order by average score
scores_average$kmer = ordered(scores_average$kmer,
                              levels=scores_average$kmer[order(scores_average$score_avg)])
scores.plot = ggplot(scores_average, aes(kmer, score_avg))+geom_point()+
  coord_flip()
```

>>>>

results = NULL
for (PTU in leading.region.PTUs){
  for (k in c(5,6)){
    scores_df = read.csv(paste0('../test_target_leading_lagging/', PTU, '_k', k, '_scores.csv'), header=T)
    n_targets = nrow(scores_df)
    scores_average <- scores_df %>%
  rowwise() %>%
  mutate(score_avg = mean(c_across(starts_with("score")))) %>%
  ungroup() %>%
  select(kmer, score_avg)
    results = rbind(results, c(PTU, k, n_targets, median(scores_average$score_avg)))
  }
}

results = data.frame(results)
colnames(results) = c("PTU", "k", "n.targets", "median.score")
results$median.score= as.numeric(results$median.score)

# Order by median score for k=6
order.k.6.scores = results[which(results$k==6), "PTU"][order(results[which(results$k==6), "median.score"])]
results$PTU = ordered(results$PTU,
                      levels=rev(order.k.6.scores))
p.depletion.targets = ggplot(results, aes(median.score, as.factor(PTU)))+
  geom_vline(xintercept = 0, size=1)+
  geom_bar(stat="identity", position="dodge")+
  facet_wrap(~k, scales="free_x")+
  ylab("")+
  xlab("Median depletion score of within-range RM targets\n(leading vs. lagging, 10kb)")+
   theme_bw()+
  theme(panel.grid = element_blank())+
  theme(axis.text=element_text(colour="black", size=12),
        axis.title.x=element_text(size=24),
        axis.text.x=element_text(size=18))+
  theme(axis.text.y=element_text(hjust=0))
ggsave(p.depletion.targets, file='../results/figure-depletion-within-range-targets.pdf',
       width=10, height=6)
```
